# Additional Learning Tasks

## 1.Write an R program to create three vectors a, b, c with 5 integers. Combine the three vectors to become a 3×5 matrix where each column represents a vector. Print the content of the matrix. Plot a graph and label correctly.
```{r}
# create 3 vectors a,b,c with 5 integers
a <- c(1,2,3,4,5)
b <- c(6,7,8,9,10)
c <- c(2,4,6,8,10)
abc_matrix <- matrix(c(a,b,c), byrow=TRUE, nrow=3)
print(abc_matrix)
matplot(abc_matrix, type='p', xlab='Row of the abc matrix', ylab='Column of the abc matrix')
```

## 2. Write a R program to create a Data frames which contain details of 5 employees and display the details. (Name, Age, Role and Length of service).
```{r}
Name <- c('Bates', 'Cornell', 'Daniels', 'Jackson', 'Somers')
Age <- c(30, 41, 40, 31, 35)
Role <- c('Accountant', 'Analyst', 'Supervisor', 'Manager', 'Director')
Length_of_service_years <- c(5, 2, 5, 5, 10)

employees <- data.frame(Name, Age, Role, Length_of_service_years)
print(employees)
```

## 3. Import the GGPLOT 2 library and plot a graph using the qplot function. X axis is the sequence of 1:20 and the y axis is the x ^ 2. Label the graph appropriately. install.packages("ggplot2", dependencies = TRUE)
```{r}
x <- 1:20
y = x^2
library(ggplot2)
qplot(x, y, geom=c('point', 'line'))

```

## 4. Create a simple bar plot of five subjects
```{r}
library(ggplot2)
Name <- c('Bates', 'Cornell', 'Daniels', 'Jackson', 'Somers')
Age <- c(30, 41, 40, 31, 35)
Role <- c('Accountant', 'Analyst', 'Supervisor', 'Manager', 'Director')
Length_of_service_years <- c(5, 2, 5, 5, 10)
employees <- data.frame(Name, Age, Role, Length_of_service_years)

ggplot(employees) +
  geom_col(aes(Name, Length_of_service_years))
```

## 5. Write a R program to take input from the user (name and age) and display the values.
```{r}
name <- readline("Hi, I'd like to know more about you. What's your name?")
name_reply <- paste("Nice to meet you", name, "!") 
print(name_reply)
age <- readline("And how old are you?")
age_reply <- paste("I hope I would be able to live till", age, "years old as well!")
print(age_reply)
```

## 6. Write a R program to create a sequence of numbers from 20 to 50 and find the mean of numbers from 20 to 50 and sum of numbers.
```{r}
numbers <- 20:50
print(mean_of_numbers <- mean(numbers))
print(sum_of_numbers <- sum(numbers))
```

## 7. Write a R program to create a vector which contains 10 random integer values between -50 and +50
```{r}
sample(-50:50, 10, replace=FALSE)
```


